% !TEX program = xelatex
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[]{vn-resume}
\newcommand*\bul{\textbullet{}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{textblock}{60}(140, 8)
  {Email:  sagarsanjeev24@gmail.com}
   \end{textblock}
  \begin{textblock}{60}(140, 12)
  {Mobile No: +91 9473422579}
   \end{textblock}
  \begin{textblock}{60}(140, 16)
LinkedIn: \href{https://www.linkedin.com/in/sagarsanjeev/}{linkedin.com/in/sagarsanjeev}%
   \end{textblock}
\namesection{Sagar Sanjeev} % NAME
{} %  TITLE
{me} % PHOTO
{}
% \profileline{}
% \vspace{\topsep}
% \vspace{5pt}
% \descript{ \bf{Summary} \\ }
% \location{Full Stack Developer with rich experience of 3 years across Data Governance in Risk and Finance Tech with Bank of America, Also a part of AI/NLP Team of Accenture Innovation Lab, worked on multiple NLP / Computer Vision based solutions for various financial and sales prospecting use cases}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\columnratio{0.3}
\begin{paracol}{2}


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     Patents
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Patents}
    \descript{{Extracting Actionable Items from Documents and Assigning them to Responsible Parties through NLP}}
    \vspace{4pt}
    \bul \location{{ US 11314938B2 } | 29\textsuperscript{th} July 2019}
    \bul \location{{ AU 2020207818A1 } | 22\textsuperscript{nd} July 2020}
    \vspace{4pt}
    \descript{{Simulation of One or More Pipeline Jobs in a Software Deployment Pipeline}}
    \vspace{4pt}
    \bul \location{{ US 20240192974A1 } | 29\textsuperscript{th} Dec 2022}
    \sectionsep


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SKILLS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \section{Skills}
    \bul \descript{Programming Languages:}
    \location{Python, C, C++, Java, Node.js}
    \bul \descript{Frontend Technologies:}
    \location{React, JavaScript, TypeScript, Angular, Svelte, HTML, CSS, Micro Frontends}
    \bul \descript{Backend Technologies:}
    \location{Flask, Express, FastAPI, Unix Scripting}
    \bul \descript{Databases:}
    \location{Oracle, MySQL, SQL Server, Neo4J, Cassandra, ElasticSearch}
    \bul \descript{Cloud \& DevOps:}
    \location{GCP, Azure, AWS, DigitalOcean, Jenkins, GitLab, Bitbucket, Autosys, Okta}
    \bul \descript{AI \& Data:}
    \location{GenAI, NLP, Knowledge Graphs, IoT}
    \sectionsep


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EDUCATION
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Education}
    \bul \descript{KIIT University}
    \qquad \location{B.Tech in Computer Science}
    \qquad \location{2014--2018}
    \sectionsep


    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     ACHIEVEMENTS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Achievements}
    \vspace{6pt}
    \begin{tightemize}
    \item \location{Awarded the Dell IT President's Award for FY26-Q4 for contributions.}
    \item \location{Awarded the ACE Award for 3 quarters in FY20 for outstanding contributions.}
    \item \location{2nd Runner-up in Financial Services Hackathon 2019 for building a Credit Decisioning using AI.}
    \item \location{Idea qualified among Top 16 in the Global Innovation Contest (GTIC) 2019.}
    \item \location{Finalist in the Global Innovation Contest (GTIC) 2020, selected from over 100,000 submitted ideas.}
    \item \location{2nd Runner-up in Project Innovation Contest 2017 at ICDCIT for ``Automation of Automobiles Using IoT.''}
    \item \location{Best Volunteer Award from National Service Scheme (NSS), KIIT University.}
    \end{tightemize}
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     CERTIFICATIONS
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Certifications}
    \vspace{4pt}
    \begin{tightemize}
    \item \location{Edureka React, 2021}
    \item \location{Neo4j Professional, 2020}
    \item \location{IBM Data Science, 2020}
    \item \location{Azure AZ-900, 2020}
    \end{tightemize}
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     COLUMN TWO
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\switchcolumn

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     SUMMARY
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Summary}
    \noindent{\small Software Engineer with 7+ years of experience building AI-powered developer tools and enterprise platforms. Patent holder in NLP and DevOps automation, with proven impact across GenAI, Knowledge Graphs, and full-stack engineering at Dell Technologies and Accenture.}
    \sectionsep

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    %     EXPERIENCE
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \section{Experience}

    \runsubsection{Dell Technologies}
    \descript{| Principal Software Engineer}
    \location{September 2021 -- Present | Bengaluru, India}
    \vspace{\topsep}
    \begin{tightemize}
    \item \location{Built an AI-powered IDE Code Assistant for VS Code integrating GenAI-based CI/CD suggestions, SDLC tooling, and automated security scans for improved developer experience.}
    \item \location{Trained and fine-tuned models for optimal CI/CD pipeline suggestions, improving automation efficiency and reducing manual configuration overhead.}
    \item \location{Designed and implemented a simulation framework for pipeline jobs (Patent Filed), reducing production job failures through proactive configuration validation and execution previews.}
    \item \location{Built a GitLab \textbf{Knowledge Graph} to deliver project-specific, context-aware code suggestions tailored to each repository.}
    \item \location{Implemented the Web version of an AI Chatbot, currently serving \textbf{1,554 users} with \textbf{200+ active monthly users}, and added support for chat-based tool access.}
    \item \location{Led enterprise-wide SSO migration from PingFederate to Okta and infrastructure migration from PCF to Kubernetes, ensuring zero-downtime transitions across 250+ active users.}
    \item \location{Created a unified IDE supporting multiple report process types to retire FlexDeploy, now used by \textbf{250+ active users} with \textbf{6,300+ reports} downloaded in the first month of enablement.}
    \item \location{Transitioned a \textbf{Monolithic} UI application into a \textbf{Micro Frontend} architecture, resulting in faster load times and improved team-level manageability.}
    \item \location{Developed automation tools for CI/CD pipelines, DevOps blueprint upgrades, and data migration from Pivotal Tracker to Jira.}
    \item \location{Built and published \textbf{36+} reusable UI components for the Dell UX Marketplace, enabling consistent design patterns across engineering teams.}
    \item \location{Implemented enterprise vulnerability management features — enabling users to track code-level vulnerabilities and raise or revoke exceptions — contributing to the resolution of \textbf{690K+} code defects.}
    \end{tightemize}
    \sectionsep

    \runsubsection{Accenture Solutions Pvt. Ltd}
    \descript{| Senior Software Developer Analyst}
    \location{April 2018 -- September 2021 | Bengaluru, India}
    \vspace{\topsep}
    \begin{tightemize}
    \item \location{Managed a data governance platform handling 30\% of the bank's metadata across 16+ lines of business (LOBs), supporting regulatory reporting and data quality standards.}
    \item \location{Operated a high-performance search tool managing \textbf{23 million+} records, enabling fast metadata discovery and lineage tracing across the enterprise.}
    \item \location{Developed NLP-powered tools including a data transformation explainer (\textbf{250K+ transformations}, saving \textbf{350+ hours} for regulatory compliance) and a fuzzy search interface enabling natural language queries with AG-Grid.}
    \item \location{Automated regulatory reporting for \textbf{FFIEC} (4 reports) and \textbf{10Q} (3 schedules), integrating them with metadata using NLP for OCC and FRB examinations.}
    \item \location{Built data and metadata visualizations using Python (NetworkX) and JavaScript (D3.js v4/6), applying graph algorithms to detect centrality, anomalies, and modularity for advanced analytics.}
    \item \location{Applied NLP techniques to scraped articles, performing open information extraction to generate insights for an AI-powered adverse media search system built on a \textbf{Knowledge Graph}.}
    \item \location{Managed end-to-end CI/CD deployments using Quartz and Jenkins, ensuring reliable and efficient integration and delivery processes.}
    \item \location{Selected for Accenture's Quick POC Development Team, delivering client-facing demos that contributed directly to new engagement wins.}
    \end{tightemize}
    \sectionsep

    \runsubsection{IoT Lab | KIIT University}
    \descript{| Junior Research Fellow}
    \location{December 2016 -- April 2018 | Bhubaneswar, India}
    \location{Created IoT proof-of-concepts, established new embedded systems, and managed Linux server administration including clustering and load balancing.}
    \sectionsep

    \runsubsection{IIT Bombay}
    \descript{| Intern}
    \location{May 2017 -- June 2017 | Mumbai, India}
    \location{Developed a simulation of network infrastructure models using Python (NetworkX) to model and analyse network operations.}
    \sectionsep

    \runsubsection{Idea Cellular Limited}
    \descript{| Intern}
    \location{May 2016 -- June 2016 | Patna, India}
    \location{Conducted staff training sessions on the newly implemented RMS system, improving adoption across the regional team.}
    \sectionsep

\end{paracol}
\end{document}
